\documentclass[10pt, a4paper]{article}

% ─── PACKAGES ────────────────────────────────────────────────────────────────
\usepackage[a4paper, top=0.9cm, bottom=0.9cm, left=0.9cm, right=0.9cm]{geometry}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{needspace}
\usepackage{paracol}
\usepackage{microtype}

% ─── FONTS ───────────────────────────────────────────────────────────────────
\setmainfont{Noto Sans}[
  BoldFont       = Noto Sans Bold,
  ItalicFont     = Noto Sans Italic,
  BoldItalicFont = Noto Sans Bold Italic
]

% ─── COLOURS ─────────────────────────────────────────────────────────────────
\definecolor{Blue}{HTML}{1A56DB}
\definecolor{Dark}{HTML}{1E293B}
\definecolor{Mid}{HTML}{334155}
\definecolor{Light}{HTML}{64748B}
\definecolor{Rule}{HTML}{CBD5E1}
\definecolor{BgHdr}{HTML}{EFF6FF}

% ─── HYPERLINKS ──────────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=Blue, linkcolor=Blue,
            pdftitle={Kamal Sroor - Senior Backend Engineer}}

% ─── SPACING ─────────────────────────────────────────────────────────────────
\linespread{1.0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{0.035\textwidth}

% ─── SECTION FORMAT ──────────────────────────────────────────────────────────
\titleformat{\section}{%
  \needspace{5\baselineskip}%
  \vspace{6pt}\raggedright\normalsize\bfseries\color{Blue}%
}{}{0em}{\MakeUppercase}[{\color{Rule}\vspace{2pt}\hrule height 0.5pt}\vspace{4pt}]

\titlespacing{\section}{0pt}{2pt}{3pt}

% ─── CUSTOM COMMANDS ─────────────────────────────────────────────────────────

% Job header: title, company, dates, location
\newcommand{\job}[4]{%
  \vspace{5pt}%
  {\bfseries\color{Dark}#1}\enspace{\color{Light}|}\enspace%
  {\bfseries\color{Blue}#2}\hfill{\footnotesize\color{Light}#3}\\%
  {\small\itshape\color{Light}#4}\vspace{2pt}%
}

% Bullet item
\newcommand{\bitem}[1]{%
  \item\small{\color{Mid}#1}%
}

% Sidebar label + value
\newcommand{\slabel}[1]{{\small\bfseries\color{Dark}#1}\\[1pt]}
\newcommand{\sval}[1]{{\small\color{Mid}#1}\\[7pt]}

% Project entry in sidebar
\newcommand{\proj}[4]{%
  {\small\bfseries\color{Dark}#1}\enspace---\enspace\href{#3}{\small\color{Blue}#2}\\[1pt]%
  {\footnotesize\color{Light}\textit{#4}}\\[6pt]%
}

% Open source entry
\newcommand{\oss}[4]{%
  {\small\bfseries\color{Dark}#1}\\[1pt]%
  {\footnotesize\itshape\color{Light}#2}\\[1pt]%
  \href{#3}{\footnotesize\color{Blue}#3}\\[2pt]%
  {\small\color{Mid}#4}\\[8pt]%
}

% List settings
\newenvironment{blist}{%
  \begin{itemize}[leftmargin=0.18in, itemsep=1pt, topsep=1pt, parsep=0pt]%
}{%
  \end{itemize}%
}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}

% ═══════════════════════════════════════════════════════════════════════════════
%  HEADER
% ═══════════════════════════════════════════════════════════════════════════════
\colorbox{BgHdr}{%
  \begin{minipage}{\dimexpr\linewidth-2\fboxsep\relax}
    \vspace{8pt}
    \begin{center}
      {\huge\bfseries\color{Dark} KAMAL SROOR}\\[4pt]
      {\large\color{Blue} Senior Backend Engineer\enspace·\enspace NestJS \& Node.js Specialist\enspace·\enspace Laravel Expert}\\[5pt]
      {\small\color{Mid}
        Cairo, Egypt\enspace·\enspace
        Open to Remote \& Relocation\enspace·\enspace
        +20 101 231 6954\enspace·\enspace
        \href{mailto:kamal.s.sroor@gmail.com}{kamal.s.sroor@gmail.com}\\[2pt]
        \href{https://www.linkedin.com/in/kamalsroor}{linkedin.com/in/kamalsroor}\enspace·\enspace
        \href{https://github.com/kamalsroor1}{github.com/kamalsroor1}
      }
    \end{center}
    \vspace{6pt}
  \end{minipage}%
}

\vspace{10pt}

% ═══════════════════════════════════════════════════════════════════════════════
%  TWO-COLUMN BODY  (63% left / 37% right)
% ═══════════════════════════════════════════════════════════════════════════════
\columnratio{0.63}
\begin{paracol}{2}

% ───────────────────────────────────────────────────────────────────────────
%  LEFT COLUMN
% ───────────────────────────────────────────────────────────────────────────

\section{Executive Profile}

{\small\color{Mid}
Self-taught engineer since age 11 with 6+ years of professional experience building
\textbf{high-availability APIs, SaaS platforms, and government digital systems} across Egypt and Saudi Arabia.
Specialised in \textbf{NestJS \& Node.js} architecture with a deep \textbf{Laravel/PHP} foundation.
Proven record of scaling systems to 10k+ DAU, reducing infrastructure costs through Redis and query optimisation,
and accelerating team delivery via AI-assisted test automation.}

\vspace{5pt}
{\small\bfseries\color{Dark}Key Highlights:}
\begin{blist}
  \bitem{\textbf{Backend Architecture:} Scalable RESTful APIs with NestJS (TypeScript), Prisma ORM, \& Laravel (PHP 8+).}
  \bitem{\textbf{Performance \& Reliability:} Redis caching, query optimisation, Docker — 10k+ DAU at 99.99\% uptime.}
  \bitem{\textbf{Testing Innovation:} AI-assisted pipeline covering 1,600+ API endpoints — over 90\% reduction in test-writing time.}
  \bitem{\textbf{DevOps:} Docker, CI/CD (GitHub Actions), AWS deployment, Nginx \& Linux administration.}
\end{blist}

% ── EXPERIENCE ───────────────────────────────────────────────────────────────
\section{Work Experience}

\job{Senior Backend Engineer}{E2E County}{Jun 2025 – Present}{Cairo, Egypt}
\begin{blist}
  \bitem{Architected migration of a decade-old Zend Framework 1 monolith to a modern Laravel ecosystem — covering \textbf{30+ modules}, \textbf{650+ database tables}, and multiple DB connections, with 100\% data integrity maintained across 6 months.}
  \bitem{Collaborated with a cross-functional team of 30+ (6 Backend, 7 Frontend, 4 QA, UI/UX) in a large-scale Agile environment, driving on-time feature delivery.}
  \bitem{Designed an \textbf{AI-assisted test automation pipeline} using Postman collections and table-level documentation; cut test-authoring time for \textbf{1,600+ API endpoints} by over \textbf{90\%}.}
  \bitem{Standardised AI prompt templates and test scripts adopted as team-wide QA practices, reducing regression cycles by 40\%.}
\end{blist}

\job{Senior Backend Engineer}{Ibtikarat}{Aug 2023 – Jun 2025}{Riyadh, Saudi Arabia (Remote)}
\begin{blist}
  \bitem{Spearheaded backend architecture for government digital transformation projects, scaling to \textbf{10k+ daily active users} at \textbf{99.99\% uptime} using Redis caching and optimised Eloquent queries.}
  \bitem{Engineered a \textbf{Multi-tenant SaaS} core with Laravel \& Livewire; integrated 5+ government APIs, expanding platform service capabilities by \textbf{40\%}.}
  \bitem{Enhanced user retention by \textbf{15\%} and increased organic traffic through OWASP security hardening and SEO structure optimisation.}
\end{blist}

\job{Backend Team Lead}{Developer Network}{Jan 2023 – Aug 2023}{Cairo, Egypt}
\begin{blist}
  \bitem{Led development of \textit{Jarvis}, a unified communication platform integrating \textbf{Meta (Facebook/WhatsApp) APIs} for enterprise customer support, onboarding 3 major clients within the first quarter.}
  \bitem{Implemented \textbf{Redis caching} and refactored Eloquent queries, achieving a \textbf{20\% reduction} in server response time across high-traffic endpoints.}
  \bitem{Mentored 3 engineers on SOLID principles, TDD, and clean architecture, reducing post-release critical bugs by \textbf{30\%}.}
\end{blist}

\job{Backend Engineer}{Pyramids Freight}{Oct 2021 – Dec 2022}{Cairo, Egypt}
\begin{blist}
  \bitem{Architected the backend for a logistics management system with complex freight calculation logic and real-time shipment tracking.}
  \bitem{Integrated \textbf{Stripe Payment Gateway} with 3D Secure, reducing payment failures by \textbf{15\%} and improving transaction success rate.}
  \bitem{Refactored legacy SQL queries and introduced database indexing, cutting average page load time by \textbf{50\%} (3s → 1.5s).}
\end{blist}

\vspace{6pt}
{\small\bfseries\color{Dark}Early Career (2019 – 2021)}\\
{\small\itshape\color{Light}Mid-Level Engineer — Abudiyab Rent A Car · ElNoor-Online · Innovation Hub · CVC · G-TECH}
\vspace{3pt}
\begin{blist}
  \bitem{Built a car rental booking engine with dynamic pricing; integrated Riyad Bank \& Mastercard payment APIs, driving a \textbf{20\% surge} in SEO-driven organic traffic.}
  \bitem{Scaled Laravel architecture supporting \textbf{30\% user growth} without infrastructure upgrades; automated CI/CD pipelines reducing release time by \textbf{20\%}.}
  \bitem{Implemented Redis caching layers improving read-heavy operations by \textbf{40\%}; standardised Swagger/OpenAPI documentation cutting third-party integration cycles by \textbf{15\%}.}
\end{blist}

% ───────────────────────────────────────────────────────────────────────────
%  RIGHT COLUMN
% ───────────────────────────────────────────────────────────────────────────
\switchcolumn

\section{Technical Skills}

\slabel{Primary Stack (Current Focus)}
{\small\bfseries\color{Blue}NestJS · Node.js · TypeScript · Prisma}\\[8pt]

\slabel{Previous Stack}
\sval{PHP 8+ · Laravel · Livewire}

\slabel{Frontend}
\sval{Vue.js · Nuxt 3 · Express.js}

\slabel{Architecture \& Patterns}
\sval{RESTful APIs · MVC · SOLID · TDD\\Domain-Driven Design · Microservices}

\slabel{Database \& Storage}
\sval{MySQL · PostgreSQL · MongoDB\\Redis (Cache/Queues) · Prisma ORM\\Eloquent ORM}

\slabel{DevOps \& Tooling}
\sval{Docker · CI/CD (GitHub Actions)\\AWS · Nginx · Linux · Git\\Kubernetes (Basics)}

\slabel{Testing \& QA}
\sval{PHPUnit · Postman\\AI-assisted automation pipelines}

\slabel{Domain Expertise}
\sval{FinTech · E-commerce · Logistics\\Government Digital Transformation}

% ── OPEN SOURCE ──────────────────────────────────────────────────────────────
\section{Open Source}

\oss{nest-scaffolding-crud-manager}%
    {NestJS · TypeScript · Prisma}%
    {https://github.com/kamalsroor1/nest-scaffolding-crud-manager}%
    {Auto-generates full CRUD modules for NestJS — controllers, services, DTOs, Prisma schema. Significantly boosts developer productivity.}

\oss{laravel-vue-modules (HMVC)}%
    {Laravel · Vue.js · HMVC · CRUD Generator}%
    {https://github.com/kamalsroor1/laravel-vue-modules}%
    {HMVC scaffolding with built-in CRUD generator — written before AI tooling existed.}

\oss{sroor-laravel-payment}%
    {Laravel · Multi-gateway}%
    {https://github.com/kamalsroor1}%
    {Open-source multi-gateway payment integration package for Laravel.}

% ── KEY PROJECTS ─────────────────────────────────────────────────────────────
\section{Key Projects}

\proj{Review App}{reviewapp.sa}{https://reviewapp.sa/}{B2B SaaS for reputation management. Increased engagement by 20\% via real-time notifications and review automation.}
\proj{Theqa App}{theqa.app}{https://theqa.app/}{Secure QA platform with OAuth2. Achieved 99.9\% availability for high-load APIs under peak traffic.}
\proj{Ettazenn}{ettazenn.com}{https://ettazenn.com/}{Health tracking ecosystem integrating wearable IoT device data via Laravel, Livewire, and custom IoT APIs.}
\proj{Al-Taawoun FC}{altaawounfc.com}{https://altaawounfc.com/}{High-traffic sports platform; maintained zero downtime during peak spikes via Redis queue management.}
\proj{Store (mapp.sa)}{mapp.sa}{https://mapp.sa/}{Scalable multi-vendor e-commerce built on multi-tenant Laravel with isolated data per merchant.}

% ── SOFT SKILLS ──────────────────────────────────────────────────────────────
\section{Soft Skills}

{\small\color{Mid}
▸ Team Leadership \& Mentoring\\[3pt]
▸ Agile / Scrum Management\\[3pt]
▸ Cross-functional Collaboration\\[3pt]
▸ Strategic Problem Solving%
}

% ── EDUCATION ────────────────────────────────────────────────────────────────
\section{Education}

{\small\bfseries\color{Dark}B.Sc.\ Management Information Systems}\\
{\small\color{Mid}New Cairo Academy · Cairo, Egypt}\\
{\small\itshape\color{Light}Graduated 2024\enspace|\enspace Self-taught engineer since 2009}

% ── CERTIFICATIONS ───────────────────────────────────────────────────────────
\section{Certifications}

{\small\color{Mid}
▸ Docker \& CI/CD — Udemy (2024)\\[3pt]
▸ Advanced PHP Optimization — Udemy (2022)\\[3pt]
▸ Laravel Certification — Laracasts (2019)%
}

% ── LANGUAGES ────────────────────────────────────────────────────────────────
\section{Languages}

{\small\color{Mid}
▸ Arabic — Native\\[3pt]
▸ English — Advanced%
}

\end{paracol}
\end{document}
