\documentclass[10pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
% تعديل الهوامش لتكون مريحة وتملأ الصفحة
\usepackage[a4paper, top=1.15cm, bottom=1.15cm, left=1cm, right=1cm]{geometry}
\usepackage{fontspec}
\usepackage[english, bidi=basic, provide=*]{babel}
\babelprovide[import, onchar=ids fonts]{english}

% Set default font to Noto Sans
\babelfont{rm}{Noto Sans}
\babelfont{sf}{Noto Sans}

% Helper packages
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{paracol} 
\usepackage{hyperref}

% زيادة تباعد الأسطر قليلاً لملء الصفحة براحة
\linespread{1.05}

% Setup Hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    filecolor=RoyalBlue,
    urlcolor=RoyalBlue,
    pdftitle={Kamal Sroor - Senior Backend Developer},
}

% Column Separation
\setlength{\columnsep}{0.04\textwidth}

% Section Formatting
\titleformat{\section}{
  \vspace{4pt}\raggedright\large\bfseries\color{RoyalBlue}
}{}{0em}{\MakeUppercase}[\color{Gray}\titlerule \vspace{4pt}]

% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{3pt}} % زيادة المسافة بين النقاط
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{10pt} % زيادة المسافة بين الوظائف لملء العمود
  \item
    \textbf{#1} \hfill {\footnotesize #2} \\ 
    \textit{\small #3} \hfill {\footnotesize #4} \\
    \vspace{4pt}
}

% Bullet point correction
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge KAMAL SROOR} \\ \vspace{5pt}
    \textbf{\Large Senior Backend Developer} \\ \vspace{5pt}
    \small
    Al Marg, Cairo, Egypt \quad $\bullet$ \quad +20 101 231 6954 \quad $\bullet$ \quad \href{mailto:kamal.s.sroor@gmail.com}{kamal.s.sroor@gmail.com} \\ \vspace{3pt}
    \href{https://www.linkedin.com/in/kamalsroor}{linkedin.com/in/kamalsroor} \quad $\bullet$ \quad 
    \href{https://github.com/Kamalsroor}{github.com/Kamalsroor}
\end{center}

\vspace{10pt}

%----------DOUBLE COLUMN START----------
\columnratio{0.65} 
\begin{paracol}{2}

%----------MAIN COLUMN (LEFT)----------

%----------SUMMARY----------
\section{Executive Profile \& Core Expertise}
Senior Backend Developer with 6+ years of experience architecting \textbf{SaaS} platforms, \textbf{Microservices}, and high-availability web applications. Expert in \textbf{PHP (Laravel)}, \textbf{SQL Performance Tuning}, and \textbf{Cloud Infrastructure}.

\vspace{5pt}
\textbf{Key Technical Highlights:}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item \textbf{System Architecture:} Designing Scalable RESTful APIs, Multi-tenant databases, and Event-driven systems.
    \item \textbf{Performance:} Caching strategies (Redis), Query Optimization, and Load Balancing.
    \item \textbf{DevOps Lifecycle:} Docker containerization, CI/CD automation (GitHub Actions), and AWS deployment.
\end{itemize}

%----------EXPERIENCE----------
\section{Work Experience}
\begin{itemize}[leftmargin=0.15in, label={}]

  % --- NEW EXPERIENCE ADDED HERE ---
    \resumeSubheading
      {Senior Backend Developer}{Jun 2025 -- Mar 2026}
      {E2E County}{Cairo, Egypt}
      \resumeItem{Led the architectural transformation of a decade-old legacy system from \textbf{Zend Framework 1} to a modern \textbf{Laravel} ecosystem, ensuring 100\% data integrity and database continuity.}
      \resumeItem{Collaborated within a large-scale agile environment including a cross-functional team of \textbf{10 Backend Developers}, 6 Frontend Developers, 4 QAs, and a dedicated UI/UX team.}
      \resumeItem{Successfully decoupled legacy business logic into modern service layers, improving system maintainability and preparing the infrastructure for future scalability.}

    \resumeSubheading
      {Senior Backend Developer}{Aug 2023 -- Jun 2025 }
      {Ibtikarat}{Riyadh, Saudi Arabia (Remote)}
      \resumeItem{Spearheaded backend architecture for government digital transformation projects, scaling systems to support \textbf{10k+ daily active users} while maintaining \textbf{99.99\% uptime}.}
      \resumeItem{Engineered a robust \textbf{Multi-tenant SaaS} core using Laravel \& Livewire, integrating 5+ third-party government APIs which expanded service capabilities by \textbf{40\%}.}
      \resumeItem{Enforced OWASP security best practices and optimized SEO structure, directly contributing to a \textbf{15\% increase} in user retention and organic traffic.}

    \resumeSubheading
      {Senior Backend Developer \& Team Leader}{Jan 2023 -- Aug 2023}
      {Developer Network}{Cairo, Egypt}
      \resumeItem{Led the development of "Jarvis," a unified communication platform integrating \textbf{Meta (Facebook/WhatsApp) APIs} for enterprise customer support.}
      \resumeItem{Optimized high-traffic endpoints by implementing \textbf{Redis caching} and refactoring Eloquent queries, achieving a \textbf{20\% reduction} in server response time.}
      \resumeItem{Mentored a team of 3 developers on \textbf{SOLID principles}, TDD, and clean architecture, reducing post-release critical bugs by \textbf{30\%}.}

    \resumeSubheading
      {Senior Backend Developer}{Oct 2021 -- Dec 2022}
      {Pyramids Freight}{Cairo, Egypt}
      \resumeItem{Architected the backend for a logistics management system, integrating complex freight calculation logic and real-time tracking.}
      \resumeItem{Implemented \textbf{Stripe Payment Gateway} with 3D Secure, streamlining transactions and reducing payment failures by \textbf{15\%}.}
      \resumeItem{Refactored legacy SQL queries and database indexing, slashing average page load times by \textbf{50\%} (from 3s to 1.5s).}

    \resumeSubheading
      {Mid-Level Backend Developer}{Jun 2021 -- Oct 2021}
      {Abudiyab Rent A Car}{Cairo, Egypt}
      \resumeItem{Developed a car rental booking engine with dynamic pricing models, integrated with \textbf{Riyad Bank} and Mastercard payment providers.}
      \resumeItem{Enhanced system observability and vehicle tracking API integrations, driving a \textbf{20\% surge} in SEO-driven traffic.}
      \resumeItem{Collaborated with mobile teams to deliver optimized API payloads, improving mobile app booking conversions by \textbf{10\%}.}

    \resumeSubheading
      {Backend Developer}{Feb 2021 -- Jun 2021}
      {ElNoor-Online}{Cairo, Egypt (Remote)}
      \resumeItem{Maintained high-availability web services, ensuring business continuity through automated health checks and error logging (Sentry).}
      \resumeItem{Optimized API response times by \textbf{25\%} through efficient data transformation and eager loading strategies.}
      \resumeItem{Standardized API documentation using \textbf{Swagger/OpenAPI}, accelerating frontend-backend integration cycles by \textbf{15\%}.}

    \resumeSubheading
      {Backend Developer}{May 2020 -- Dec 2020}
      {Innovation Hub}{Riyadh, Saudi Arabia (Remote)}
      \resumeItem{Designed a scalable Laravel architecture supporting a \textbf{30\% user base growth} without infrastructure upgrades.}
      \resumeItem{Modernized legacy codebases, reducing technical debt and improving maintainability scores by \textbf{40\%}.}
      \resumeItem{Automated deployment workflows using \textbf{CI/CD pipelines}, reducing release times by \textbf{20\%} and eliminating manual errors.}

    \resumeSubheading
      {Team Leader \& Full Stack Developer}{Nov 2019 -- May 2020}
      {CVC}{Cairo, Egypt}
      \resumeItem{Managed a cross-functional Agile team of 5, ensuring \textbf{100\% on-time delivery} for client projects through effective sprint planning.}
      \resumeItem{Conducted code reviews and technical workshops, elevating code quality standards across the department.}

    \resumeSubheading
      {Backend Developer}{Jul 2019 -- Nov 2019}
      {G-TECH}{Cairo, Egypt}
      \resumeItem{Developed modular PHP components, reducing development time for subsequent modules by \textbf{25\%}.}
      \resumeItem{Implemented Redis caching layers, improving data retrieval performance by \textbf{40\%} for read-heavy operations.}

\end{itemize}

%----------SIDEBAR START (RIGHT)----------
\switchcolumn

%----------HARD SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=4pt]
    \small{
     \item \textbf{Languages \& Frameworks:} \\ PHP 8+, Laravel, Livewire, Node.js, Express.js, Vue.js, Nuxt 3, TypeScript.
     \item \textbf{Architecture \& Patterns:} \\ Microservices, MVC, RESTful APIs, SOLID, TDD (PHPUnit), Domain-Driven Design (DDD).
     \item \textbf{Database \& Storage:} \\ MySQL, PostgreSQL, Redis (Caching/Queues), MongoDB, Eloquent ORM.
     \item \textbf{DevOps \& Tools:} \\ Docker, Kubernetes (Basics), CI/CD (GitHub Actions), AWS, Nginx, Linux, Git.
    }
\end{itemize}

%----------SOFT SKILLS----------
\section{Soft Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=3pt]
    \small
    \item Team Leadership \& Mentoring
    \item Strategic Problem Solving
    \item Agile/Scrum Project Management
    \item Cross-functional Collaboration
\end{itemize}

%----------PROJECTS (SIDEBAR)----------
\section{Key Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Review App} $|$ \href{https://reviewapp.sa/}{reviewapp.sa} \\
    \footnotesize \textit{Laravel, Vue.js, MySQL} \\
    \textbf{Scope:} B2B SaaS for reputation mgmt. \\
    \textbf{Impact:} +20\% engagement via real-time notifs.
    \vspace{6pt}
    
    \item \textbf{Theqa App} $|$ \href{https://theqa.app/}{theqa.app} \\
    \footnotesize \textit{PHP, Secure API, OAuth2} \\
    \textbf{Scope:} Secure QA platform. \\
    \textbf{Impact:} 99.9\% availability for high-load APIs.
    \vspace{6pt}

    \item \textbf{Ettazenn} $|$ \href{https://ettazenn.com/}{ettazenn.com} \\
    \footnotesize \textit{Laravel, Livewire, IoT APIs} \\
    \textbf{Scope:} Health tracking ecosystem. \\
    \textbf{Impact:} Integrated wearable device data.
    \vspace{6pt}

    \item \textbf{Al-Taawoun FC} $|$ \href{https://altaawounfc.com/}{altaawounfc.com} \\
    \footnotesize \textit{Laravel, Redis, High-Traffic} \\
    \textbf{Impact:} Zero downtime during traffic spikes.
    \vspace{6pt}

    \item \textbf{Store Platform} $|$ \href{https://mapp.sa/}{mapp.sa} \\
    \footnotesize \textit{Multi-tenant Laravel} \\
    \textbf{Scope:} Scalable multi-vendor e-commerce.
    \vspace{4pt}
    
    \item \textbf{Sroor-Laravel-Payment} \\
    \footnotesize \href{https://github.com/Kamalsroor/sroor-laravel-payment}{GitHub Package} \\
    Open-source payment integration package.
\end{itemize}

\section{Other Projects}
\small
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=3pt]
    \item \href{https://hazelspaces.com/}{Hazel Spaces}
    \item \href{https://www.rafeeg.ae/}{Rafeeg}
    \item \href{https://www.pyramidsfreight.com/}{Pyramids Freight}
    \item \href{https://www.madariskm.com/}{Madariskm LMS}
    \item \href{https://wsa-events.com/}{WSA Events}
    \item \href{https://oliviaclinics.com/}{Olivia Clinics}
    \item \href{https://wsa-elite.com/}{WSA Elite}
    \item \href{https://www.abudiyab-soft.com/}{Abudiyab Soft}
\end{itemize}

%----------EDUCATION----------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{B.Sc. Management Information Systems} \\
    New Cairo Academy \\
    Cairo, Egypt \\
    2020 -- 2024
\end{itemize}

%----------CERTIFICATIONS----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item Docker \& CI/CD (2024)
    \item Advanced PHP Optimization (2022)
    \item Laravel Certification (2019)
\end{itemize}

%----------LANGUAGES----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item Arabic (Native)
    \item English (Advanced)
\end{itemize}

\end{paracol}
\end{document}
